Flabby and injective objects in toposes

### 2018-10-20 paper-flabby-objects.tex
typo

A sheaf~$F$ on a topological space (or locale)~$X$ is \emph{flabby} (flasque) if and only
if all restriction maps~$F(X) \to F(U)$ are surjective. The following
properties of flabby sheaves render them fundamental to the theory of sheaf
cohomology:
% XXX: Je nachdem, wie die Einleitung aussieht, hier die Betonung anders
% setzen. Fundamental ist nur, dass man welke Auflösungen zur Berechnung von
% Garbenkohomologie verwenden kann und dass sie von f_* bewahrt werden. Die
% restlichen Eigenschaften sind wichtig, aber nicht fundamental.
\begin{enumerate}
\item Let~$(U_i)_i$ be an open covering of~$X$.
A sheaf~$F$ on~$X$ is flabby if and only if all of its restrictions~$F|_{U_i}$
are flabby as sheaves on~$U_i$.
\item Let~$f : X \to Y$ be a continuous map. If~$F$ is a flabby sheaf on~$X$,
then~$f_*(F)$ is a flabby sheaf on~$Y$.
\item[(3)] Let~$0 \to F \to G \to H \to 0$ be a short exact sequence of sheaves of
modules.
\begin{enumerate}
\item If~$F$ is flabby, then this sequence is also exact as a sequence of
presheaves.
\item If~$F$ and~$H$ are flabby, then so is~$G$.
\item If~$F$ and~$G$ are flabby, then so is~$H$.
\end{enumerate}
\item[(4a)] Any sheaf can be embedded into a flabby sheaf.
\item[(4b)] Any sheaf of modules can be embedded into a flabby sheaf of modules.
\end{enumerate}

@@

\begin{prop}\label{prop:basics-injective}
\begin{enumerate}
% Take care if numbering changes (referenced below)
\item Any set can be embedded into an injective set.
\item Any injective module is also injective as a set.
\item Assuming the axiom of choice, any module can be embedded into an
injective module.
\end{enumerate}\end{prop}

\begin{proof}\begin{enumerate}
\item One can check that, for instance, the full powerset~$\P(X)$ and the set of
subterminals~$\P_{\leq 1}(X)$ are each injective.~\cite{XXX}
\item The forgetful functor from modules to sets possesses a left exact left
adjoint. More explicitly, if~$i : A \to B$ is an injective map between sets and
if~$f : A \to I$ is an arbitrary map, then the induced map~$R\langle A \rangle
\to R\langle B \rangle$ between free modules is also injective, the given
map~$f$ lifts to a linear map~$R\langle A \rangle \to I$, and an~$R$-linear
extension~$R\langle B \rangle \to I$ induces an extension~$B \to M$ of~$f$.
\item One verifies that any abelian group can be embedded into a divisible
abelian group. By Baer's criterion (which requires the axiom of choice), divisible abelian groups are injective.
The result for modules over arbitrary rings then follows purely
formally~\cite{XXX}. \qedhere
\end{enumerate}\end{proof}

@@

\begin{scholium}\label{scholium:properties-of-flabby-objects}
For any elementary topos~$\E$:
\begin{enumerate}
\item Any object can be embedded into an internally injective object.
\item (If~$\E$ has a natural numbers object.) The underlying unstructured
object of an internally injective module is internally injective.
\item Any internally injective object is flabby.
% Take care if numbering changes (referenced below).
\item Any object can be embedded into a flabby object.
\item The terminal object is flabby. The product of flabby objects is flabby.
\item Let~$I$ be an internally injective object. Let~$T$ be an arbitrary
object. Then~$[T,I]$ is a flabby object.
\item (If~$\E$ has a natural numbers object.) Let~$I$ be an internally
injective~$R$-module. Let~$T$ be an arbitrary~$R$-module. Then~$[T,I]_R$, the
subobject of the internal Hom consisting only of the linear maps, is a flabby
object.
\item Let~$0 \to M' \to M \to M'' \to 0$ be a short exact sequence
of~$R$-modules in~$\E$. If~$M'$ and~$M''$ are flabby objects, so is~$M$.
\end{enumerate}
\end{scholium}

@@

\begin{prop}\label{prop:semienough-flabby-modules}
Assuming the law of excluded middle in the metatheory, any~$\neg\neg$-separated
module in the effective topos can be embedded into a flabby module.
\end{prop}

>>>>

A sheaf~$F$ on a topological space (or locale)~$X$ is \emph{flabby} (flasque) if and only
if all restriction maps~$F(X) \to F(U)$ are surjective. The following
properties of flabby sheaves render them fundamental to the theory of sheaf
cohomology:
% XXX: Je nachdem, wie die Einleitung aussieht, hier die Betonung anders
% setzen. Fundamental ist nur, dass man welke Auflösungen zur Berechnung von
% Garbenkohomologie verwenden kann und dass sie von f_* bewahrt werden. Die
% restlichen Eigenschaften sind wichtig, aber nicht fundamental.
\begin{enumerate}
\item Let~$(U_i)_i$ be an open covering of~$X$.
A sheaf~$F$ on~$X$ is flabby if and only if all of its restrictions~$F|_{U_i}$
are flabby as sheaves on~$U_i$.
\item Let~$f : X \to Y$ be a continuous map. If~$F$ is a flabby sheaf on~$X$,
then~$f_*(F)$ is a flabby sheaf on~$Y$.
\item[(3)] Let~$0 \to F \to G \to H \to 0$ be a short exact sequence of sheaves of
modules.
\begin{enumerate}
\item If~$F$ is flabby, then this sequence is also exact as a sequence of
presheaves.
\item If~$F$ and~$H$ are flabby, then so is~$G$.
\item If~$F$ and~$G$ are flabby, then so is~$H$.
\end{enumerate}
\item[(4a)] Any sheaf embeds into a flabby sheaf.
\item[(4b)] Any sheaf of modules embeds into a flabby sheaf of modules.
\end{enumerate}

@@

\begin{prop}\label{prop:basics-injective}
\begin{enumerate}
% Take care if numbering changes (referenced below)
\item Any set embeds into an injective set.
\item Any injective module is also injective as a set.
\item Assuming the axiom of choice, any module embeds into an
injective module.
\end{enumerate}\end{prop}

\begin{proof}\begin{enumerate}
\item One can check that, for instance, the full powerset~$\P(X)$ and the set of
subterminals~$\P_{\leq 1}(X)$ are each injective.~\cite{XXX}
\item The forgetful functor from modules to sets possesses a left exact left
adjoint. More explicitly, if~$i : A \to B$ is an injective map between sets and
if~$f : A \to I$ is an arbitrary map, then the induced map~$R\langle A \rangle
\to R\langle B \rangle$ between free modules is also injective, the given
map~$f$ lifts to a linear map~$R\langle A \rangle \to I$, and an~$R$-linear
extension~$R\langle B \rangle \to I$ induces an extension~$B \to M$ of~$f$.
\item One verifies that any abelian group embeds into a divisible
abelian group. By Baer's criterion (which requires the axiom of choice), divisible abelian groups are injective.
The result for modules over arbitrary rings then follows purely
formally~\cite{XXX}. \qedhere
\end{enumerate}\end{proof}

@@

\begin{scholium}\label{scholium:properties-of-flabby-objects}
For any elementary topos~$\E$:
\begin{enumerate}
\item Any object embeds into an internally injective object.
\item (If~$\E$ has a natural numbers object.) The underlying unstructured
object of an internally injective module is internally injective.
\item Any internally injective object is flabby.
% Take care if numbering changes (referenced below).
\item Any object embeds into a flabby object.
\item The terminal object is flabby. The product of flabby objects is flabby.
\item Let~$I$ be an internally injective object. Let~$T$ be an arbitrary
object. Then~$[T,I]$ is a flabby object.
\item (If~$\E$ has a natural numbers object.) Let~$I$ be an internally
injective~$R$-module. Let~$T$ be an arbitrary~$R$-module. Then~$[T,I]_R$, the
subobject of the internal Hom consisting only of the linear maps, is a flabby
object.
\item Let~$0 \to M' \to M \to M'' \to 0$ be a short exact sequence
of~$R$-modules in~$\E$. If~$M'$ and~$M''$ are flabby objects, so is~$M$.
\end{enumerate}
\end{scholium}

@@

\begin{prop}\label{prop:semienough-flabby-modules}
Assuming the law of excluded middle in the metatheory, any~$\neg\neg$-separated
module in the effective topos embeds into a flabby module.
\end{prop}
